---
title: Supplement material for Climate change drives shifts in straddling fish stocks in the world's ocean
subtitle: "Juliano Palacios-Abrantes, Thomas Frölicher, Gabriel Reygondeau, Bianca S. Santos, U. Rashid Sumaila, Colette C. C. Wabnitz & William W. L. Cheung"
output: 
 pdf_document:
toc: 
lof: no
lot: no
number_sections: no
header-includes:
   - \usepackage{caption}
---
\captionsetup{width=6in}

\begin{flushleft}
{\LARGE \textbf{List of Supplementary Materials:}}
\begin{itemize}
\item \textbf{Figures:} S1 - S8
\item \textbf{Tables:} S1 - S3
\end{itemize}
\end{flushleft}



```{r setup, include=FALSE, eval = T}

knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')


# These libraries are only needed for examples in the introduction 
library("png")
library("grid")
# These are needed in case you are having a glossary
library("knitr")
library("kableExtra")
library("dplyr")
library("tibble")
library("readr")


```


\clearpage

\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}

# Supplementary Figures



```{r changes_early_high, eval = T, echo = T, echo=FALSE, fig.height=4, fig.width=8, fig.pos= "H", fig.cap="Percentage of total straddling stocks per region projected to undergo significant changes in stock share ratio (SSR) between Exclusive Economic Zones (EEZs) and the high seas by 2030 under the high emissions scenario. A) Arrows indicate stocks shifting from EEZs to the high seas, (B) Arrows indicate stocks shifting from the high seas to EEZs. Values represent the percentage of stocks experiencing significant SSR shifts relative to the total number of straddling stocks in each region. The width of each arrow link width corresponds to the proportion of stocks shifting, with wider links indicating a larger proportion. Arrows are color-coded by region for clarity. Abbreviations: C = Central; E = Eastern; N = North; S = Southern; T = Temperate; Tr = Tropical; W = West. See table S1 for a list of EEZs within each region.", out.extra=''}

# Call the image
img <- readPNG("fig_S1.png")

# Print the image
grid.raster(img)
```


```{r changes_mid, eval = T, echo = T, echo=FALSE, fig.height=10, fig.width=10, fig.pos="H", fig.cap="Changes in straddling stock share ratio (SSR) between Exclusive Economic Zones (EEZ) and the high seas by the middle of the 21st century under both scenarios. A) Shifts from EEZ to the high seas under the low emission scenario, B) shifts from the high seas to EEZ under low emisison scenario, C) shifts from EEZ to the high seas under high emsission scenario, D) shifts from the high seas to EEZ, under high emission scenario. Values represent the percentage of stocks experiencing significant SSR shifts relative to the total number of straddling stocks in each region. Arrows represent directionality and width percentage of stocks shifting to the neighboring zone (EEZ/high seas). The width of each arrow link width corresponds to the proportion of stocks shifting, with wider links indicating a larger proportion. Arrows are color-coded by region for clarity. Abbreviations: C = Central; E = Eastern; N = North; S = Southern; T = Temperate; Tr = Tropical; W = West. See table S2 for a list of EEZs within each region. ", out.extra=''}

# Call the image
img <- readPNG("fig_S2.png")

# Print the image
grid.raster(img)
```

```{r net_changes_eezs, eval = T, echo = T, echo=FALSE, fig.height=10, fig.width=10, fig.pos = "H", fig.cap="Net changes in Stock Share Ratio (SSR) between Exclusive Economic Zones (EEZ) and the high seas by the middle of the 21st century under both scenarios. A) Shifts by 2030 under the low emission scenario, B) Shifts by 2030 under high emsission scenario, C) shifts by 2050 under the low emission scenario, B) shifts by 2050 under high emsission scenario. Links colored by region. Net changes = stock gains - stock losses. Numbers on the axis and size of links represent the percentage of stocks shifting and the arrow shows the direction of the shift.", out.extra=''}

# Call the image
img <- readPNG("fig_S3.png")

# Print the image
grid.raster(img)
```


```{r net_changes, eval = T, echo = T, echo=FALSE, fig.height=10, fig.width=10, fig.pos="H", fig.cap="Average percentage change in Stock Share Ratio (SSR) across commercial groups within EEZs by the mid 21st century. Positive changes indicate an increase in the proportion of stocks within EEZs (yellow), while negative changes indicate an increase in the proportion of stocks in the high seas (green). Error bars represent the standard deviation of SSR changes across shifting stocks within each commercial group. Only commercial groups with shifting stocks are shown for each time period. Abbreviations: C = Central; E = Eastern; N = North; S = Southern; T = Temperate; Tr = Tropical W = West.", out.extra=''}

# Call the image
img <- readPNG("fig_S4.png")

# Print the image
grid.raster(img)
```


```{r net_changes_rfmo, eval = T, echo = T, echo=FALSE, fig.height=10, fig.width=10, fig.pos = "H", fig.cap="Net changes in Stock Share Ratio (SSR) of highly migratory straddling stocks between neighboring Regional Fisheries Management Organizations (RFMOs). A) By 2030 under the high emission scenario, B) by 2050 under the low emission scenario, C) by 2050 under the high emission scenario. Links colored by RFMO. Net changes = stock gains - stock losses. Numbers on the axis and size of links represent the percentage of stocks shifting and the arrow shows the direction of the shift. The Commission for the Conservation of Southern Bluefin Tuna (CCSBT), The Inter-American Tropical Tuna Commission (IATTC), The International Commission for the Conservation of Atlantic Tunas (ICCAT), The Indian Ocean Tuna Commission (IOTC), and The Western and Central Pacific Fisheries Commission (WCPFC).", out.extra=''}

# Call the image
img <- readPNG("fig_S5.png")

# Print the image
grid.raster(img)
```


```{r treshold, eval = T, echo = T, echo=FALSE, fig.height = 4, fig.width = 7, fig.pos= "H", fig.align='center',fig.cap="Sensitivity analysis for spatial threshold. Each level represents a minimum percentage of occurrence between Region and the high seas. For example, the 10\\% threshold means that both the Region and the the high seas have at least 10\\% of the shared stock. For this study we used the 10\\% (red) threshold, the 0\\% (gray) represents no threshold. Analysis done with GFDL under low emission scenario at the early time period (see methods)", out.extra=''}

# Call the image
img <- readPNG("fig_S6.png")

# Print the image
grid.raster(img)
```


```{r rfmo_map, eval = T, echo = T, echo=FALSE, fig.height = 3,fig.width=8, fig.pos= "h", fig.cap="Map showing the five different tuna RFMO and EEZs classifications according to the marine realm established by Spalding et al 2009. The Commission for the Conservation of Southern Bluefin Tuna (CCSBT), The Inter-American Tropical Tuna Commission (IATTC), The International Commission for the Conservation of Atlantic Tunas (ICCAT), The Indian Ocean Tuna Commission (IOTC), and The Western and Central Pacific Fisheries Commission (WCPFC). Note that CCSBT has no defined convention area, thus, for this analysis, CCSBT area has been considered the areas south of IATTC, ICCAT, IOTC and WCPFC convention areas’ southern limits.", out.extra=''}

# Call the image
img <- readPNG("fig_S7.png")

# Print the image
grid.raster(img)
```


```{r n_transboundary, eval = T, echo = T, echo=FALSE, fig.height = 5, fig.width=9, fig.pos= "H", fig.cap="Map showing the number of transboundary species (n = 633) present in each cell of the world (4). Gridcell scale 0.5 latitude by 0.5 longitude. The original 633 species were then used to estimate the number of straddling stocks.", out.extra=''}

# Call the image
img <- readPNG("fig_S8.png")

# Print the image
grid.raster(img)
```





\clearpage

# Supplementary Tables

```{r table_straddling, eval = T, echo = F, message = FALSE}

readr::read_csv(here::here('./results/supplements/straddling_species.csv')) %>% 
  dplyr::select(
    `Scientific name` = taxon_name,
    `Common name` = common_name,
    `Commercial group` = commercial_group
  ) %>% 
  kable("latex",
        caption = "List of straddling species identified in the present study grouped by “commercial group” based on the Sea Around Us classification.",
        booktabs = TRUE,
        # col.names = NULL,
        longtable = TRUE) %>% # needed if glossary extends one page
  column_spec(1, width = "2cm") %>%  # Size of first column
  column_spec(1,italic = TRUE, bold = F) %>% # Abbreviation bold 
  sub("\\\\toprule", "", .) %>% # removes top border
  sub("\\\\bottomrule", "", .)  # removes bottom border

```

The global EEZ shapefile (updated 1 July 2015) and the RFMOs shapefiles were provided by SAU (Available from https ://www.seaaroundus.org). It is important to note that the data subdivides the EEZs of 198 coastal states into 280 regions (e.g., Mexico’s EEZ is divided in Mexico Pacificand Mexico Atlantic), including islands territories. Finally, the MEOW shapefile according to Spalding et al (2007) was provided by World Widlife Fund and The Nature Conservancy (Available from https://www.worldwildlife.org/publications/marine-ecoregions-of-the-world-a-bioregionalization-of-coastal-and-shelf-areas). 

```{r table_realm_eez, eval = T, echo = F, message = FALSE}

readr::read_csv(here::here('./results/supplements/realm_to_eez.csv')) %>% 
  dplyr::rename(`Exclusive Economic Zone` = EEZ) %>% 
  kable("latex",
        caption = "List of Exclusive Economic Zones (EEZs) according to the Sea Around Us (www.searoundus.org) and their Realm according to Spalding et al (2006).",
        booktabs = TRUE,
        # col.names = NULL,
        longtable = TRUE) %>% # needed if extends one page
  column_spec(1, width = "2cm") %>%  # Size of first column
  column_spec(1,italic = TRUE, bold = F) %>% # Abbreviation bold
  sub("\\\\toprule", "", .) %>% # removes top border
  sub("\\\\bottomrule", "", .) # removes bottom border
  


```


```{r table_rpackages, eval = T, echo = F, message = FALSE}


data.frame(
  "Package" = c(
    "readxl", # Read dataframe
    "data.table", # Read dataframe (Fast!)
    "wesanderson",
    "tidyverse", # for all data wrangling and ggplot
    "janitor", # for data cleaning
    "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
    "ggrepel", # for nice plot labels
    "sf", #Spatial analysis 
    "sp", #Spatial analysis 
    "doParallel", # for parallelization
    "rfishbase", # for species ecosystem affinity
    "zoo", #for runing mean
    "rnaturalearth", # For maps
    "R.matlab", # For Gabs distributions
    "viridis",
    "circlize"
  ),
  "Source" = c(
   "Wickham, H. and Bryan, J., 2022. Package readxl; Read Excel Files. CRAN.",
   "Dowle, M. and Srinivasan, A., 2022. Package data.table; Extension of “data.frame.” CRAN.",
   "Ram, K., Wickham, H., Richards, C. and Baggett, A., 2018. Package wesanderson; A Wes Anderson Palette Generator. CRAN.",
   "Wickham, H., 2022. Pakcage tidyverse; Easily Install and Load the “Tidyverse.” CRAN.",
   "Firke, S., Haid, C., Knight, R. and Denney, B., 2018. Package janitor; Simple tools for examining and cleaning dirty data. CRAN.",
   "Queiroz, G. D., Hvitfeldt, E., Keyes, O., Misra, K., Mastny, T., Erickson, J., Robinson, D. and Silge, J., 2019. Package tidytext; Text Mining using “dplyr”, “ggplot2”, and Other Tidy Tools. CRAN.",
   "Slowikowski, K., 2020. Package ggrepel: Automatically Position Non-Overlapping Text Labels with “ggplot2.” CRAN.",
   "Pebesma, E., 2022. Package sf; Simple Features for R. CRAN.",
   "Pebesma, E. and Bivand, R., 2023. Package sp; Classes and methods for Spatial Data. CRAN.",
   "Daniel, F. and Weston, S., 2022. doParallel: Foreach Parallel Adaptor for the “parallel” Package. CRAN.",
   "Boettiger, C., Chamberlain, S., Lang, D. T. and Wainwright, P., 2019. Package rfishbase; R Interface to “FishBase”. CRAN.",
   "Zeileis, A., Grothendieck, G., Ryan, J. A., Ulrich, J. M. and Andrews, F., 2019. Package zoo; S3 Infrastructure for Regular and Irregular Time Series (Z’s Ordered Observations). CRAN.",
   "Massicott, P. and South, A., 2023. Package rnaturalearth; World Map Data from Natural Earth. CRAN.",
   "Bengtsson, H., Jacobson, A. and Riedy, J., 2018. Package R.matlab: Read and Write MAT Files and Call MATLAB from Within R. CRAN.",
   "Garnier, S., 2018. Package viridis; Colorblind-Friendly Color Maps for R. CRAN.",
   "circlize"
    )
) %>% kable("latex",
        caption = "List of R packages used in the current study.",
        booktabs = TRUE,
        # col.names = FA,
        longtable = TRUE) %>% # needed if glossary extends one page
  column_spec(1, width = "2cm") %>%  # Size of first column
  column_spec(2, width = "14cm") %>%  # Size of first column
  sub("\\\\toprule", "", .) %>% # removes top border
  sub("\\\\bottomrule", "", .)  # removes bottom border

```