---
title: "Untitled"
author: "Juliano Palacios-Abrantes"
date: '2022-04-20'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

library(MyFunctions)

packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  "cowplot", # for figures 1 and 3
  # "ggimage", #for reading images to the circular plot
  "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  # "spdep", # for poly2nb old
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  # "purrr",#Spatial analysis
  # "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "parallel", # for parallelization
  "doParallel", # for parallelization
  # "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo", #for runing mean
  # "pgirmess", # for dune test after kurtis wallas
  "rnaturalearth", # For maps
  "R.matlab", # For Gabs distributions
  "parallel",
  "viridis",
  # Juanitos map
  "zeallot",
  "geosphere",
  # Sankey network
  "networkD3",
  "circlize"
)

my_lib(packages)

# Fix new updates of sf package
sf::sf_use_s2(use_s2 = FALSE)
```


# Methods

1.- Get transboundary species list

1.1- Remove highly migratory species based on literature

2- High seas shapefile

2.1- FAO Areas ID

3.- Identiy what transboundary species are actually straddling 

4.- Be happy, happy like a hippo

# Data

## Shapefiles 

```{r shapefiles, eval = F}

# World land maps
world_land <- ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = 4326)# 4326

# Coordinatres DBEM
coords_dbem <- my_path("Spa","DBEM","Lon_Lat_DBEM.txt",read = T, header = F)
colnames(coords_dbem) <- c("index","lon","lat")

dbem_sf <-st_as_sf(coords_dbem,
                   coords = c("lon", "lat")
) %>% 
  st_set_crs(4326) #%>%
# st_transform(crs = "+proj=eck4")

st_crs(dbem_sf) = 4326

# EEZs
# world_eez <- my_sf("SAU",simple = 1000)

# SAU index table
sau_index_code <- my_data("sau_index")

### Get MEO to DBEM

meow_regions <- my_sf("MEOW")
st_crs(meow_regions) = 4326

meow_dbem <- st_join(dbem_sf,
                     meow_regions,
                     join = st_intersects)


# Get eez per realm
dbem_meow_df <- meow_dbem %>% 
  as.data.frame() %>% 
  select(-geometry) %>% 
  clean_names() %>% 
  filter(!is.na(realm))


# dbem_meow_df %>%
#   left_join(coords_dbem) %>%
#   ggplot() +
#   geom_tile(
#     aes(
#       x = lon,
#       y = lat,
#       fill = realm
#     )
#   )


# RFMO regions
# RFMO data
sf_rfmo <- my_sf("RFMO") %>% 
  filter(RFMO_nm_s %in% c("ICCAT","WCPFC","IOTC","IATTC","CCSBT")) %>% 
  dplyr::rename(rfmo_name = RFMO_nm_s) %>% 
  group_by(rfmo_name) %>% 
  summarise(geometry = st_union(geometry))

st_crs(sf_rfmo) = 4326

rfmo_dbem <- st_join(dbem_sf,
                     sf_rfmo,
                     join = st_intersects)

# Select only high seas (i.e., remove waters within EEZs)
rfmo_dbem_hs <- rfmo_dbem %>% 
  as.data.frame()%>% 
  select(-geometry) %>% 
  clean_names() %>% 
  filter(!is.na(rfmo_name)) # remove areas where no tuna RFMO exists (some high seas pockets)


# Finalize data
dbem_rfmo_index <- rfmo_dbem_hs %>% 
  filter(!index %in% dbem_meow_df$index)
  

# dbem_rfmo_index %>%
#   left_join(coords_dbem) %>%
#   ggplot() +
#   geom_tile(
#     aes(
#       x = lon,
#       y = lat,
#       fill = rfmo_name
#     )
#   ) +
#   geom_tile(data = dbem_meow_df %>% left_join(coords_dbem),
#     aes(
#       x = lon,
#       y = lat
#     ),
#     fill = "red"
#   )

write_csv(dbem_rfmo_index, my_path("Spa", "SAU/SAU_RFMO/","RFMO_Index_Code.csv"))





## Coombine rfmo and MEOW shapefiles in one


sf_rfmo_to_combine <- sf_rfmo %>% 
  select(region = rfmo_name, geometry)

sf_meow_to_combine <- meow_regions %>% 
  select(region = REALM, geometry)
  
sf_meow_rfmo <- rbind(sf_rfmo_to_combine, 
                      sf_meow_to_combine)




```

## Determine adjacent RFMOs and MEOWS

Code modified from FishForVisa

```{r funEstNeighbours, eval = F, echo=T}

Shapefile = sf_meow_rfmo

  # Get sparse matrix
int = suppressMessages(st_intersects(Shapefile))
  # Warnning message
  # although coordinates are longitude/latitude, st_intersects assumes that they are planar
  
  
  # Intitalize new object
  mat = NULL
  
  # Fill
  for(i in 1:NROW(int)){
    #Create matrix with ID and intersecting IDs
    tmp = cbind(i, int[[i]])
    
    # Join to Initalized object
    mat  = rbind(mat, tmp)
  }
  
  # Build final data.frame substituting ID for name (in this case nc$name)
  Result_table = data.frame(region = Shapefile$region[mat[,1]], 
                            adjacent_region = Shapefile$region[mat[,2]]
                            )
  
  # Remove duplicates... eg of course an object intersects with itself...
  Result_table = Result_table[Result_table$region != Result_table$adjacent_region,]
  
 # Get index cells within those RFMOs
  rfmo_partial <- Result_table %>% 
        rename(rfmo_name = region) %>% 
    left_join(rfmo_dbem, 
                  by = "rfmo_name")%>% 
    filter(!is.na(index)) %>% 
    rename(region = rfmo_name)
  
  # Get index cells within those MEOWS
  meow_partial <- Result_table %>% 
        rename(realm = region) %>% 
    left_join(meow_dbem_grid, 
                  by = "realm") %>% 
    filter(!is.na(index)) %>% 
    rename(region = realm)
  
  rfmo_meow_final <- bind_rows(rfmo_partial,meow_partial) %>% 
    group_by(region,adjacent_region) %>% 
    tally() %>% 
    select(-n)
  
  
  write_csv(rfmo_meow_final, my_path("G","Spatial/SAU/SAU_RFMO/","rfmo_meow_neighbours.csv"))
  
  
  
```

## Determining straddling stocks

```{r GetSppDistFun, eval = F}

# Spp = 600066

GetSppDist=function(Spp,Model,Coord){
  
  Data_Path <- my_path("G","FishForVisa")  
  Distpath <- paste(Data_Path,"Data/Distribution/",sep="")
  INDEX = seq(1,259200,1)
  # INDEX <- Coordinates$INDEX
  
  # SAU Distributions
  if(Model == "SAU_D"){
    File_Name <- paste("SAU_Distribution/DIST_GOOD_SP_")
  }
  
  # SAU Catch
  if(Model == "SAU_C"){
    File_Name <- paste("SAU_data_per_species/CATCH_SP_")
  }
  
  # Occurence
  if(Model == "Occ"){
    File_Name <- paste("Occurence/OCCURENCE_JULIANO_")
  }
  
  # ENM Model
  if(Model == "ENM"){
    File_Name <- paste("ENM/ENM_JULIANO_")
  }
  
  # DBEM Data
  # if(Model == "DBEM"){
  #   Distpath <- "/Volumes/DATA/JULIANO_NEYMAR/PristineSeasData
  #   Final_Path <- "ENM"
  #   File_Name <- paste("ENM_JULIANO",Spp,".mat",sep="")
  # }
  
  if(Model == "All"){
    
    Models_List <- c(paste(Distpath,"SAU_Distribution/DIST_GOOD_SP_",Spp,".mat",sep =""),
                     paste(Distpath,"Occurence/OCCURENCE_JULIANO_",Spp,".mat",sep=""),
                     paste(Distpath,"ENM/ENM_JULIANO_",Spp,".mat",sep="")
    )
    
    # Jumps species not modeled. NOTE: We only need one as ENM, Occ and SAU Dis have all the same 939 spp
    if(file.exists(Models_List[1])){
      
      Load <- lapply(Models_List, FUN=R.matlab::readMat, na.strings=0)
      
      sppdist <- as.data.frame(bind_cols(Load)) %>% 
        mutate(
          INDEX = INDEX,
          TaxonKey = Spp
        )
      colnames(sppdist) <- c("SAU_D","Occ","ENM","INDEX","TaxonKey")
      
      #### Step for SAU catch data that has to be averaged
      File_Name <- paste("SAU_data_per_species/CATCH_SP_")
      SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
      
      # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
      SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
        select(CATCH.1:CATCH.65) %>% 
        mutate(INDEX = INDEX) %>% 
        gather("Year","Catch",CATCH.56:CATCH.65) %>% # Last 10 years of data
        group_by(INDEX) %>% 
        summarise(SAU_C = mean(Catch,na.rm=T))
      
      # Join both tables
      sppdist <- sppdist %>% 
        left_join(SAU_C_data,
                  by = "INDEX") %>% 
        select(TaxonKey,INDEX,everything()) %>% 
        left_join(CoorG,
                  by = "INDEX")
      
      # Fix coordinate system incompatibility between Gab and DBEM
      sppdist <- suppressWarnings(sppdist[order(sppdist$latitude, rev(sppdist$longitude),decreasing=TRUE), ] %>% 
                                    mutate(INDEX = seq(1,259200,1)) %>% 
                                    gather("Model","Value",3:6) %>%
                                    mutate(Value = ifelse(is.na(Value), 0, Value)) # Converting NA's to ceros
      )
      
      getSppDist = sppdist
      
    }
    
  }else{  
    
    # Merge paths
    SppPath <- paste(Distpath,File_Name,Spp,".mat",sep="")
    
    if(file.exists(SppPath) == TRUE){
      
      #Install (if needed) R.matlab package
      if(!require(R.matlab)){
        install.packages("R.matlab")
      }
      
      # Read Files
      
      sppdist <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
        mutate(INDEX = INDEX,
               Species = Spp) %>% 
        left_join(Coord) 
      
      # Fix coordinate system incompatibility between Gab and DBEM
      sppdist <- sppdist[order(sppdist$latitude, rev(sppdist$longitude),decreasing=TRUE), ] %>% 
        mutate(INDEX = seq(1,259200,1))
      
      # Return 
      getSppDist=sppdist
      
    }else{
      print(paste("No info for this species",Spp, "in",Model))
    }
    
  }
}
```


```{r StraddIndexFun, eval = F}

# Spp = 600006

StraddIndex <- function(Spp, Model = "All", Neighbours, Coord, Index_Code, treshold = F){
  
  # Get model data from spps
  SppDist <- GetSppDist(Spp,Model,Coord)
  
  
  # ggplot(SppDist %>% filter(Value >0)) +
  #   geom_tile(
  #     aes(
  #       x = longitude,
  #       y = latitude,
  #       fill = Value,
  #       color = Value
  #     )
  #   ) +
  #   facet_wrap(~Model) +
  #   geom_sf(data = rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")))
  
  
  
  # Result 1. Number of Countries that share the species
  
  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(Model != "SAU_C") %>% 
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
    group_by(TaxonKey, INDEX) %>%
    summarise(Model_Index = sum(Value,na.rm=T)/3,
              .groups = "drop") %>%
    # filter(Model_Index > 0.4) %>% # at least 2 sources agree
    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
    left_join(SppDist,
              by = c("TaxonKey","INDEX")) %>%
    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
           Value > 0) %>%
    # mutate(Model_Index = Model_Index*100) %>%
    select(-Model, -Value, -latitude,-longitude,-Model_Index) %>%
    rename(index = INDEX) %>% 
    
    # Trans_Spp %>%
    #   left_join(coords_dbem) %>%
    #   ggplot() +
    #   geom_tile(
    #     aes(x = lon,
    #         y = lat,
    #         fill = index)
    #   ) +
    #   geom_tile( data = Trans_Spp %>% left_join(coords_dbem) %>% filter(index %in% c(72227,72228,72946)),
    #       aes(x = lon,
  #         y = lat),
  #       fill = "red"
  #     )
  
  # joint eez names
  left_join(meow_dbem_grid, # No EEZs but MEOWs
            by = "index") %>% 
    # joint rfmo area names
    left_join(rfmo_index,
              by = "index") %>% 
    mutate(
      region = ifelse(is.na(rfmo_name),realm,rfmo_name),
      category = ifelse(!is.na(rfmo_name),"rfmo","realm"),
    ) %>%
      select(1:3,region,category) %>%
      clean_names()
    
    ### ----------  Distributional test  ---------- ###
    # test <- Trans_Spp %>%
    # left_join(coords_dbem) #%>% 
    # filter(is.na(territory))
    
    # sau_index_code %>% filter(eez_name != "High seas") %>% 
    #   left_join(coords_dbem) %>% 
    #   ggplot() +
    #   geom_tile(
    #     aes(
    #       x = lon,
    #       y = lat
    #     ),
    #     fill = "red"
    #   ) + 
    #   geom_tile(data = meow_dbem_grid %>% left_join(coords_dbem),
    #     aes(
    #       x = lon,
    #       y = lat,
    #       # fill = rfmo_name
    #     ),
    #     fill = "black"
    #   ) + 
    #   geom_sf(data = sf_land, aes())
    
    # 
    # ggplot(test) +
    #   geom_tile(
    #     aes(
    #       x = lon,
    #       y = lat,
    #       fill = territory
    #     )
    #   ) +
    #   geom_sf(data = sf_land, aes())
    
    
    ### ----------------------------------- ###
    
    # Get realms and RFMOs
    rfmo_to_realm <- Neighbours %>% 
      filter(region %in% c(Trans_Spp %>% filter(category == "rfmo") %>% pull(region) %>% unique()),
             adjacent_region %in% c(Trans_Spp %>% filter(category == "realm") %>% pull(region) %>% unique()))
    
    
    #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
    # The number of species' cells present within each REALM and RFMO
    
    Spp_Grid <- Trans_Spp %>% 
      group_by(taxon_key,
               region,
               category) %>% 
      summarise(n_cells_territory = length(unique(index)),
                .groups = "drop")
    
    # Split dataframes to merge latter
    Territory_T <- Spp_Grid %>% 
      filter(category == "realm") %>% 
      ungroup() %>% 
      select(
        taxon_key,
        Name=region,
        n_cells_territory
      )
    
    Neighbour_T <- Spp_Grid %>%
      filter(category == "rfmo") %>% 
      ungroup() %>% 
      select(
        taxon_key,
        n_cells_territory,
        Name=region
      ) 
    
    
    rfmo_grid <- Spp_Grid %>% 
      filter(category == "rfmo") %>% 
      left_join(rfmo_to_realm,
                by = "region") %>% 
      select(Name = adjacent_region,
             rfmo_name = region,
             n_cells_territory)
    
    # Merge dataframes to get totals per Neighbourds
    Area_Index_D <-
      full_join(Territory_T,
                Neighbour_T, 
                by = c("Name","taxon_key")
      ) %>%
      left_join(rfmo_grid,
                by ="Name") %>% 
      filter(!is.na(rfmo_name)) %>% # remove non-straddling stocks
      rowwise() %>%
      mutate(spp_total = sum(n_cells_territory.x,n_cells_territory,na.rm=T)) %>% # Total gridcelles per Neighbours
      distinct() %>% # Removes false duplicates from `full_join()`
      rename(realm = Name,
             n_cells_realm = n_cells_territory.x,
             n_cells_rfmo = n_cells_territory) %>%
      # Estimate if it is straddling by counting the percentage of the distribution in the RFMO
      mutate(area_rfmo = (n_cells_rfmo/spp_total)*100,
             area_realm = (n_cells_realm/spp_total)*100
             )
    
    
    output <- Area_Index_D %>% 
      select(taxon_key,
             realm,
             rfmo_name,
             area_rfmo,
             area_realm)
    
    File_Name <- paste(Spp,"_straddling.csv",sep = "")
    Save_Path <- my_path("R","Straddling_realm_rfmo", File_Name)
    
    if(nrow(output) >0){
      
      write_csv(output,
                Save_Path)
      
      return(print(paste("Completed analysis for taxon key",Spp)))
    }else{
      return(print(paste("Taxon key",Spp,"is not a straddling stock")))
    }
    
  } # closes treshold ifstatement
  
} # closes function

```


### Control pannel

```{r control_pannel, eva = F}

# Gabriel's coordinate system 
CoorG <- my_path("G","FishForVisa/Data/Spatial/","coordinates_gab.csv",read =T) %>%
  mutate(INDEX = seq(1,259200,1))

# RFMO data
rfmo_index <- my_path("Spa","/SAU/SAU_RFMO/","RFMO_Index_Code.csv", read = T)

# DBEM to MEOW grid
meow_dbem_grid <- my_path("Spa","MEOW", "meow_dbem_grid.csv", read = T) %>% 
  clean_names()

# Neighboring RFMOs and MEOWs created in previous chunk on July 20
rfmo_meow <- my_path("G","Spatial/SAU/SAU_RFMO/","rfmo_meow_neighbours.csv", read = T) # Neighbours

# Load FishForVisa Results
transboundary_spp <- read_csv("https://media.githubusercontent.com/media/jepa/FishForVisa/master/Data/Results/Clean_Results_Trans.csv") %>% 
  # Set same filters as in FishForVisa
  filter(
    area_index >= 0.25,
    area_index <= 1-0.25,
    model_index >= 100
  )

# Double check we have 633 species
length(unique(transboundary_spp$taxon_key)) # 633

#Get DBEM coords 
coords_dbem <- my_data("dbem_coords")

# Species to ran
run_species <- list.files(my_path("R","Straddling_realm_rfmo"))
run_species <- str_sub(run_species,1,6)

run_me <- transboundary_spp %>% 
  filter(!taxon_key %in% run_species) %>% 
  pull(taxon_key) %>% 
  unique()


# Exx to region to Rfmo  DF

eez_rfmo_region <- dbem_sf %>% 
  left_join(sau_index_code) %>% 
  filter(eez_id > 0) %>% 
  st_join(sf_meow) %>% 
  group_by(eez_name,region = realm) %>% 
  tally() %>% 
  as.data.frame() %>% 
  left_join(rfmo_meow,
            by = "region") %>% 
  select(eez_name,region,adjacent_region) %>% 
  na.omit()

write(eez_rfmo_region, my_path("D","Spatial",name = "eez_rfmo_region.csv"))

```


Methodological points to consider

- RFMOs neighboring realms from the MEOW
- The straddling index accounts for how much of the population is present (as a %) in the RFMO. So if it says 80%, it means that 80% of the population is present in the RFMO and 20% in the realm.
- A straddling stock is herein defined as a stock that is shared between a REALM (and its EEZs) and a RFMO.


```{r run_me, eval = F}

# One species
# StraddIndex(Spp = 600069,
#             Model = "All",
#             Coord = coords_dbem, 
#             Index_Code = sau_index_code,
#             Neighbours = rfmo_meow,
#             treshold = T
#             )

# All species lapply
# lapply(run_me, 
#        StraddIndex, 
#        Model = "All", 
#        Coord = coords_dbem, 
#        Index_Code = sau_index_code, 
#        Neighbours = rfmo_meow,
#        treshold = T)



cl <- makeCluster(10) # total 12
# registerDoSNOW(cl)

repetitions <- length(run_me)
pb <- txtProgressBar(max = repetitions, style = 3)

progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress = progress)


foreach(i=1:repetitions,
        .combine = rbind,
        .packages = "tidyverse",
        .options.snow = opts,
        .verbose = T) %dopar% 
  StraddIndex(
    run_me[i],
    Model = "All",
    Coord = coords,
    Index_Code = sau_index_code,
    Neighbours = rfmo_meow,
    tresh = T
  )

close(pb)
stopCluster(cl)
gc()

```


## Estimating Proportion change

### Functions

This function simply reads all results of straddling stocks (see previous step)

```{r Fun_GetTransResults, eval = T}

GetResults=function(Spp,type = "strad"){
  
  if(type == "strad"){
    # Set the path for each file
    Distpath <- paste(my_path("R","Straddling_realm_rfmo/"),Spp,"_straddling.csv",sep="")
  }else{
    Distpath <- paste(my_path("R","Per_change_realm_rfmo/"),Spp,"_perchg.csv",sep="")
  }
  
  # Loads all files in a df
  Load_Data <- bind_rows(lapply(Distpath, FUN=fread))
  
  if(nrow(Load_Data)>0){
    
    return(Load_Data)
  }
}


```

This function is the main analysis estimating the proportion change above historic levels

```{r estimate_proportion, eval = F}
# 

# taxon_key <- 600006

taxon_proportion <- function(taxon_key, dbem_grid){
  
  print(taxon_key)
  
  stradd_data <- GetResults(taxon_key)
  # category <- unique(stradd_data$cat)
  
  rfmo_areas <- stradd_data %>% 
    pull(rfmo_name) %>% 
    unique()
  
  files_path <-list.files(my_path("G","dbem/dbem_cmip6/r_data"),full.names = T)[-3] # remove GFDL45B
  
  to_read <- paste0(taxon_key,"Abd.RData")
  
  for(m in 1:6){
    # m = 1
    #################################
    # List esm folders
    file_to_read <- paste0(files_path[m],"/",to_read)
    print(file_to_read)
    if(file.exists(file_to_read)){
      
      load(file_to_read)
      
      # Transform it to df--
      
      
      if(exists("sppabdfnl")){
        spp_data <- as.data.frame(sppabdfnl) %>% 
          rowid_to_column("index")
        colnames(spp_data) <- c("index", seq(1951, 2100, 1))
        rm(sppabdfnl) 
      }else{
        spp_data <- as.data.frame(data) %>% 
          rowid_to_column("index")
        colnames(spp_data) <- c("index", seq(1951, 2100, 1))
        rm(data) 
      }
      
      
      # Get area of analysis
      taxon_rfmo_dbem_area <-stradd_data %>%
        pivot_longer(c(realm,rfmo_name)) %>% 
        pull(value) %>% 
        unique()
      
      # Get ammount abundance per region
      spp_data_area <-spp_data %>% 
        gather("year","value",`1951`:`2100`) %>%
        left_join(dbem_grid,
                  by = c("index")
        ) %>% 
        left_join(rfmo_index,
                  by = "index",
                  relationship = "many-to-many") %>% 
        mutate(name = ifelse(is.na(realm),rfmo_name,realm)) %>% 
        filter(name %in% taxon_rfmo_dbem_area) %>%
        group_by(year,name) %>% 
        summarise(total_zone_abd = sum(value,na.rm = T),
                  .groups = "drop") %>% 
        mutate(taxon_key = as.integer(taxon_key))
      
      # Estimate proportions of each region
      
      # RFMO values
      rfmo_values <- spp_data_area %>% 
        filter(name %in% stradd_data$rfmo_name) %>% 
        rename(rfmo_total_zone_abd = total_zone_abd,
               rfmo_name = name) %>% 
        left_join(stradd_data,
                  by = c("rfmo_name","taxon_key"),
                  relationship = "many-to-many") %>% 
        rename(realm_name = realm)
      
      # Realms values
      realm_values <- spp_data_area %>% 
        filter(name %in% stradd_data$realm) %>% 
        rename(realm_total_zone_abd = total_zone_abd,
               realm_name = name)
      
      
      # combine both regions to estimate proportions
      spp_proportion <- left_join(rfmo_values,realm_values,
                                  by = join_by("year", "taxon_key","realm_name")
      ) %>% 
        mutate(region_total = rfmo_total_zone_abd+realm_total_zone_abd) %>% 
        mutate(per_rfmo = rfmo_total_zone_abd/region_total*100) %>%  # done with RFMO 
        filter(region_total >0) # Remove cases where there is no catch data in any area
      
      # How it looks
      # ggplot(spp_proportion) +
      #   geom_area(
      #     aes(
      #       x = as.numeric(year),
      #       y = per_rfmo,
      #       fill = realm
      #       # fill = high_mig_spa
      #     )
      #   ) +
      #   facet_wrap(~rfmo_name)
      
      
      # Estimate changes in abd proportion
      
      # Early proportions
      hs_historical_means <- spp_proportion %>% 
        filter(year <= 2014) %>%
        group_by(taxon_key,rfmo_name,realm_name) %>% 
        summarise(hs_mean = mean(per_rfmo, na.rm = T),
                  hs_sd = sd(per_rfmo, na.rm = T),
                  .groups = "drop") %>%
        mutate(top_tresh = hs_mean+2*hs_sd,
               low_tresh = hs_mean-2*hs_sd) %>% 
        select(-hs_mean,-hs_sd)
      
      # Estimate future proportions that overshoot the mean =- 2 sd
      prop_chng <- spp_proportion %>% 
        mutate(period = ifelse(year >2021 & year <2040,"ear",
                               ifelse(year > 2041 & year <2060,"mid",NA)
        )
        ) %>% 
        filter(!is.na(period)) %>% 
        group_by(taxon_key,rfmo_name,realm_name,area_rfmo,area_realm,period) %>% 
        summarise(mean = mean(per_rfmo, na.rm = T),
                  sd = sd(per_rfmo, na.rm = T),
                  .groups = "drop") %>% 
        left_join(hs_historical_means,
                  by = c("taxon_key","rfmo_name","realm_name"),
                  relationship = "many-to-many") %>% 
        mutate(change = ifelse(mean > top_tresh,"gain",
                               ifelse(mean < low_tresh,"lost","same")
        )
        ) 
      
      
      # Incorporate rcp and esm info to data
      # str_count(files_path[m]) # 90
      
      final_data <- prop_chng %>% 
        mutate(esm = str_to_lower(str_sub(files_path[m],80,83)),
               rcp = paste0("rcp",str_sub(files_path[m],84,85)),
               esm = ifelse(esm == "mpi2","mpi", ifelse(esm == "mpi8","mpi",esm)), # Fix MPI
               rcp = ifelse(rcp == "rcp6F","rcp26", ifelse(rcp == "rcpBF","rcp85",rcp)), # Fix MPS
        ) %>% 
        select(taxon_key,esm,rcp,period,rfmo_name,change,realm_name,low_tresh,mean,top_tresh,area_rfmo,area_realm)

      
      if(m == 1){
        final_output <- final_data
      }else{
        final_output <- bind_rows(final_output,final_data)
      }
      
      
    } # Close models for loop
    
  }
  
  # Save file
  name_file <- my_path("R","Per_change_realm_rfmo", paste0(taxon_key,"_perchg.csv"))
  write_csv(final_output, name_file)
  return(paste("Data for",taxon_key, "saved"))
  
}

# taxon_proportion(600006)
# gc()
```

### Control pannel for RFMO to realm

```{r get_straddling, eval = F}

# Get fao areas on DBEM grid
# fao_area_grid <- my_path("Spa", "DBEM","fao_to_dbem_grid.csv", read = T) 
meow_dbem_grid <- my_path("Spa","MEOW", "meow_dbem_grid.csv", read = T) %>% 
  clean_names() %>% 
  select(index,realm)

# meow_dbem_grid %>% left_join(coords_dbem) %>% 
#   ggplot() +
#   geom_tile(
#     aes(
#       x = lon,
#       y = lat,
#       fill = realm
#     )
#   )


# RFMO data (REQUIRED)
rfmo_index <- my_path("Spa","/SAU/SAU_RFMO/","RFMO_Index_Code.csv", read = T)


# Spp list
spp_complete <- list.files(my_path("R","Straddling_realm_rfmo/"))
stradling_spp <- str_replace(spp_complete,"\\_.*","")

# Species to ran
ran_species <- list.files(my_path("R","Per_change_realm_rfmo"))
ran_species <- str_sub(ran_species,1,6)

# Run reminindg species
run_me_list <- stradling_spp[!(stradling_spp %in% ran_species)]



# stradd_data <- bind_rows(
#   lapply(stradling_spp,GetResults)
# ) %>% 
#   mutate(taxon_key = as.character(taxon_key))


# For Lauren
# dbem_index <- my_data("sau_index") %>% 
#   left_join(meow_dbem_grid) %>% 
#   group_by(eez_name,realm) %>% 
#   tally() %>% 
#   filter(!is.na(realm))

# write.csv(dbem_index, "eez_to_realm.csv")

```


### Proportion estimate

```{r proportion_call, eval = F}

# Single species
# taxon_proportion(taxon_key = 600069)

# Multiple speices in one
# suppressMessages(
#   lapply(stradling_spp[1:2],
#          taxon_proportion)
# )

#Multiple species in parallel
suppressMessages(
  mclapply(run_me_list,
           taxon_proportion,
           dbem_grid = meow_dbem_grid,
           mc.cores = detectCores()-2)
)


```


### Control pannel for RFMO to RFMO


```{r}

rfmo_taxon_proportion <- function(taxon_key){
  
  print(taxon_key)
  
  stradd_data <- GetResults(taxon_key)
  # category <- unique(stradd_data$cat)
  
  rfmo_areas <- stradd_data %>% 
    pull(rfmo_name) %>% 
    unique()
  
  files_path <-list.files(my_path("G","dbem/dbem_cmip6/r_data"),full.names = T)
  
  to_read <- paste0(taxon_key,"Abd.RData")
  
  for(m in 1:6){
    # m = 1
    #################################
    # List esm folders
    file_to_read <- paste0(files_path[m],"/",to_read)
    
    if(file.exists(file_to_read)){
      
      load(file_to_read)
      
      # Transform it to df--
      spp_data <- as.data.frame(sppabdfnl) %>% 
        rowid_to_column("index")
      colnames(spp_data) <- c("index",(seq(1951,2100,1)))
      rm(sppabdfnl) # remove original load
      
      
      # Get amount abundance per region
      spp_data_area <- spp_data %>%
        gather("year","value",`1951`:`2100`) %>%
        left_join(rfmo_index,
                  by = c("index"
                  ),
                  relationship = "many-to-many"
        ) %>% 
        # left_join(rfmo_index,
        #           by = "index",
        #           relationship = "many-to-many") %>% 
        # mutate(name = ifelse(is.na(region),rfmo_name,region)) %>% 
        filter(rfmo_name %in% rfmo_areas) %>%
        group_by(year,rfmo_name) %>% 
        summarise(total_rfmo_abd = sum(value,na.rm = T),
                  .groups = "drop") %>% 
        mutate(taxon_key = as.integer(taxon_key))
      
      # Estimate proportions of each region
      
      # RFMO values
      # rfmo_values <- spp_data_area %>% 
      #   filter(name %in% stradd_data$rfmo_name) %>% 
      #   rename(rfmo_total_zone_abd = total_zone_abd,
      #          rfmo_name = name) %>% 
      #   left_join(stradd_data,
      #             by = c("rfmo_name","taxon_key"),
      #             relationship = "many-to-many") %>% 
      #   rename(region_name = region)
      
      
      # Get neighbors 
      
      
      neighbour_data <- spp_data_area %>% 
                    rename(neighbour = rfmo_name, neighbour_abd = total_rfmo_abd)
      
      rfmo_values_neigh <-
        spp_data_area %>% 
        rename(territory = rfmo_name) %>% 
        left_join(rfmo_neighbour,
                  by = "territory",
                  relationship = "many-to-many") %>% 
        rename(territory_abd = total_rfmo_abd) %>% 
        left_join(neighbour_data,
                  by = c("year", "taxon_key", "neighbour") 
                  ) %>% 
        # remove potential sameless
        mutate(
          same = ifelse(territory == neighbour,"same","not")
        ) %>% 
        filter(same == "not") %>% 
        select(- same)
        
      
      # combine both regions to estimate proportions
      spp_proportion <- rfmo_values_neigh %>% 
        mutate(region_total = territory_abd+neighbour_abd) %>% 
        mutate(per_rfmo_t = territory_abd/region_total) %>%  # done with RFMO 
        mutate(per_rfmo_n = neighbour_abd/region_total) %>%  # done with RFMO 
        filter(region_total >0) # Remove cases where there is no catch data in any area
      
      # How it looks
      # spp_proportion %>% 
      #   # filter(territory == "IATTC") %>% 
      # ggplot() +
      #   geom_area(
      #     aes(
      #       x = as.numeric(year),
      #       y = per_rfmo_t#,
      #       # fill = neighbour
      #       # fill = high_mig_spa
      #     )
      #   ) +
      #   facet_wrap(territory~neighbour)
      
      
      # Estimate changes in abd proportion
      
      # Early proportions
      hs_historical_means <- spp_proportion %>% 
        filter(year <= 2014) %>%
        group_by(taxon_key,territory,neighbour) %>% 
        summarise_at(
          c("per_rfmo_t","per_rfmo_n"),
          c(mean = "mean",
            sd = "sd"), na.rm = T
          ) %>%
        mutate(top_tresh_t = per_rfmo_t_mean+2*per_rfmo_t_sd,
               low_tresh_t = per_rfmo_t_mean-2*per_rfmo_t_sd,
               top_tresh_n = per_rfmo_n_mean+2*per_rfmo_n_sd,
               low_tresh_n = per_rfmo_n_mean-2*per_rfmo_n_sd) %>% 
        select(-per_rfmo_t_mean:-per_rfmo_n_sd)
      
      # Estimate future proportions that overshoot the mean =- 2 sd
      prop_chng <- spp_proportion %>% 
        mutate(period = ifelse(year >2021 & year <2040,"ear",
                               ifelse(year > 2041 & year <2060,"mid",NA)
        )
        ) %>% 
        filter(!is.na(period)) %>% 
        group_by(taxon_key,territory,neighbour,period) %>% 
        summarise_at(
          c("per_rfmo_t","per_rfmo_n"),
          mean, na.rm = T
                     ) %>% 
        left_join(hs_historical_means,
                  by = c("taxon_key","territory","neighbour"),
                  relationship = "many-to-many") %>% 
        mutate(change_t = ifelse(per_rfmo_t > top_tresh_t,"gain",
                               ifelse(per_rfmo_t < low_tresh_t,"lost","same")
        ),
        change_n = ifelse(per_rfmo_n > top_tresh_n,"gain",
                               ifelse(per_rfmo_n < low_tresh_n,"lost","same")
        )
        ) 
      
      
      # Incorporate rcp and esm info to data
      # str_count(files_path[m]) # 90
      
      final_data <- prop_chng %>% 
        mutate(esm = str_to_lower(str_sub(files_path[m],80,83)),
               rcp = paste0("rcp",str_sub(files_path[m],84,85)),
               esm = ifelse(esm == "mpi2","mpi", ifelse(esm == "mpi8","mpi",esm)),
               rcp = ifelse(rcp == "rcp6F","rcp26", ifelse(rcp == "rcp5F","rcp85",rcp)),
        ) %>% 
        select(taxon_key,esm,rcp,period,rfmo_t = territory, low_tresh_t,change_t,top_tresh_t,
               rfmo_n = neighbour,low_tresh_n,change_n,top_tresh_n)
      
      if(m == 1){
        final_output <- final_data
      }else{
        final_output <- bind_rows(final_output,final_data)
      }
      
      
    } # Close models for loop
    
  }
  
  
  if(nrow(final_output) > 0){
  # Save file
  name_file <- my_path("R","Per_change_rfmo_rfmo", paste0(taxon_key,"_perchg.csv"))
  write_csv(final_output, name_file)
  return(paste("Data for",taxon_key, "saved"))
  }else{
    return(paste("No shared data for",taxon_key))
  }
  
}

# rfmo_taxon_proportion(600006)
# gc()
```


```{r get_straddling, eval = F}


coords_dbem <- my_data("dbem_coords")

# RFMO on DBEM grid (meow_dbem_grid)
rfmo_grid <- my_path("Spa",extra_path = "SAU/SAU_RFMO", name = "RFMO_Neighbours_List.csv", read = T) %>% 
  filter(territory %in% c("ICCAT","WCPFC","IOTC","IATTC","CCSBT"),
         neighbour%in% c("ICCAT","WCPFC","IOTC","IATTC","CCSBT")) %>% 
  clean_names() 

# RFMO neighbours
rfmo_neighbour <- rfmo_grid %>% 
  group_by(territory,neighbour) %>% 
  tally() %>% 
  select(-n)

# RFMO index
rfmo_index <- my_path("Spa","/SAU/SAU_RFMO/","RFMO_Index_Code.csv", read = T)


# rfmo_index %>% left_join(coords_dbem) %>%
#   ggplot() +
#   geom_tile(
#     aes(
#       x = lon,
#       y = lat,
#       fill = rfmo_name
#     )
#   )


# Spp list
spp_complete <- list.files(my_path("R","Straddling_realm_rfmo/"))
stradling_spp <- str_replace(spp_complete,"\\_.*","")

stradd_data <- bind_rows(
  lapply(stradling_spp,GetResults)
) %>% 
  mutate(taxon_key = as.character(taxon_key))


# For Lauren
# dbem_index <- my_data("sau_index") %>% 
#   left_join(meow_dbem_grid) %>% 
#   group_by(eez_name,realm) %>% 
#   tally() %>% 
#   filter(!is.na(realm))

# write.csv(dbem_index, "eez_to_realm.csv")

```


### Proportion estimate

```{r proportion_call, eval = F}


# taxon_proportion(taxon_key = 600069)



# suppressMessages(
#   lapply(stradling_spp[1:2],
#          taxon_proportion)
# )

# Parallelization


suppressMessages(
  mclapply(stradling_spp,
           rfmo_taxon_proportion,
           mc.cores = detectCores()-2)
)

```


# Results

## Data needed

```{r Fun_GetTransResults, eval = T}

GetResults=function(Spp,type = "strad"){
  
  if(type == "strad"){
    # Set the path for each file
    Distpath <- paste(my_path("R","Straddling_realm_rfmo/"),Spp,"_straddling.csv",sep="")
  }else{
    Distpath <- paste(my_path("R","Per_change_realm_rfmo/"),Spp,"_perchg.csv",sep="")
  }
  
  # Loads all files in a df
  Load_Data <- bind_rows(lapply(Distpath, FUN=fread))
  
  if(nrow(Load_Data)>0){
    
    return(Load_Data)
  }
}


```

```{r results_data, eva = T}

#-----------------# 
## Georeferenced ##
#-----------------# 

# SAU relations between INDEX and Country's EEZs
# sau_index_code <- my_data("sau_index")

#world land 
sf_land <- ne_countries(scale = 'large', returnclass = c("sf")) %>%
  st_transform(crs = 4326)

# meows
sf_meow <- my_sf("MEOW") %>% 
  clean_names()
st_crs(sf_meow) = 4326

# RFMO regions
sf_rfmo <- my_sf("RFMO_tuna",simple = 1)

# SAU shapefile
# sf_eez <- my_sf("SAU", simple = 0.1)

# SAU index table
sau_index_code <- my_data("sau_index")

# SAU eez to fishing entity
sau_matching_names <- read.csv("~/Library/CloudStorage/OneDrive-UBC/Data/Spatial/SAU/sau_matching_names.csv") %>% 
  select(sf_eez_name,fishing_entity = sau_fishing_entity,iso_a3)


#-----------------# 
## Spp related   ##
#-----------------# 

# List of SAU species
exploited_spp <- my_path("G","Species", "exploited_species_list.csv", read = T)

## Straddling species ##
# Spp list
# spp_complete <- list.files(my_path("R","Straddling_realm_rfmo/"))
# stradling_spp <- str_replace(spp_complete,"\\_.*","")

# Get straddling stocks
# shared_data <- bind_rows(
#   lapply(stradling_spp,GetResults, type = "strad")
# ) %>% 
#   left_join(exploited_spp) #%>% 
  # mutate(category = ifelse(taxon_name %in% un_species$scientific_name,"strad","high_mig"))

# Get proportion analysis
spp_complete <- list.files(my_path("R","Per_change_realm_rfmo/"))
stradling_spp <- str_replace(spp_complete,"\\_.*","")

partial_straddling_df <- bind_rows(
  lapply(stradling_spp,GetResults, type = "strad")
  ) %>% 
  rename(realm_name = realm
         )

length(unique(partial_straddling_df$taxon_key))# 103

# Get straddling stocks
prop_data_esm <- bind_rows(
  lapply(partial_straddling_df$taxon_key,GetResults, type = "prop")
  ) %>% 
  # Include area index info
  left_join(partial_straddling_df,
            by = c("taxon_key","rfmo_name","realm_name")
        ) %>% 
  filter(area_rfmo > 10,
         area_rfmo < 90) %>% 
  # Remove species not present in high seas
  filter(
    low_tresh != 0 &
      mean != 0 &
      top_tresh != 0,
    low_tresh != 100 &
      mean != 100 &
      top_tresh != 100
           ) %>% 
  left_join(exploited_spp) 


prop_data <- prop_data_esm %>%
  # Re- estimate change with average of all ESMs
  group_by(taxon_key,taxon_name,common_name,rcp,period,rfmo_name,realm_name) %>% 
  summarise_at(
    .vars = c("low_tresh","mean","top_tresh"),
    .funs = mean,
    na.rm = T) %>% 
  mutate(change = ifelse(mean > top_tresh,"gain",
                               ifelse(mean < low_tresh,"lost","same")
        )
  )

length(unique(prop_data$taxon_key))# 76


#### Catch data

# rfmo_list <- c(my_path("D","SAU/catch/ccsbt","SAU RFMO 3 v50-1.csv", read = F),
#   my_path("D","SAU/catch/iattc", "SAU RFMO 5 v50-1.csv", read = F),
#   # my_path("D","SAU/catch/iccat",),
#   my_path("D","SAU/catch/iotc","SAU RFMO 7 v50-1.csv", read = F),
#   my_path("D","SAU/catch/wcpfc","SAU RFMO 18 v50-1.csv")
# )

# suppressMessages(
# rfmo_catch <- bind_rows(
#   lapply(rfmo_list, read_csv)) %>%
#   filter(scientific_name %in% unique(prop_data$taxon_name)) %>%
#   group_by(area_name,year,scientific_name,common_name,commercial_group,fishing_entity) %>%
#   #adds up gear type, fishing sectors, catch type and reporting
#   summarise_at(.vars = c("tonnes","landed_value"),
#                .funs = sum) %>%
#   # Average last 10 years of data
#   filter(year >= 2007) %>%
#   group_by(area_name,scientific_name, common_name,commercial_group,fishing_entity) %>%
#   summarise_at(.vars = c("tonnes","landed_value"),
#                .funs = mean,
#                na.rm = T) %>%
#   filter(!(common_name == "Indian mackerel" & fishing_entity == "Thailand"),
#          !(common_name == "Japanese anchovy" & fishing_entity %in% c("China","Japan")),
#          !(common_name == "Short mackerel" & fishing_entity == "Indonesia")
#          ) #remove wrong data as per personal communication with Deng P.
# ) %>%
#   mutate(commercial_group = ifelse(is.na(commercial_group),"Other fishes & inverts",commercial_group),
#          commercial_group = ifelse(scientific_name %in% c("Clupea harengus","Regalecus glesne"),"Herring-likes",
#                                    ifelse(scientific_name %in% c("Glyptocephalus cynoglossus","Hippoglossoides platessoides","Hippoglossus hippoglossus"),"Flat-fish",
#                                           commercial_group)
#          )
#   )


sau_groups <- read.csv("./results/supplements/straddling_species.csv")

```

## Straddling identification

### Straddling treshold supplements

```{r threshold_sensitivity, eval = F}

 bind_rows(
  lapply(straddling_spp,GetResults, type = "prop")
  ) %>% 
  filter(
    rcp == "rcp26",
    period == "ear",
    esm == "gfdl"
  ) %>% 
  # Include area index info
  left_join(partial_straddling_df,
            by = c("taxon_key","rfmo_name","realm_name")
        ) %>% 
  mutate(thresh_level = 
           ifelse(area_rfmo > 30 & area_rfmo < 70, "30%",
                  ifelse(area_rfmo > 20 & area_rfmo < 80, "20%",
                         ifelse(area_rfmo > 10 & area_rfmo < 90, "10%","No threshold")
                  )
           ),
         combo = paste(realm_name,rfmo_name, sep = "-")
  ) %>% 
  # View()
  group_by(combo,thresh_level) %>%
  # group_by(realm_name,rfmo_name,thresh_level) %>%
  tally() %>%
  ggplot() +
  geom_bar(
    aes(
      x = reorder(combo,desc(combo)),
      y = n,
      fill = thresh_level
    ),
    stat = "identity",
    position = position_stack(reverse = T)
  ) +
  labs(
    x = "Region and RFMO combination",
    y = "Number of straddling stocks"
  ) +
  coord_flip() +
  # facet_wrap(~ realm_name) +
  scale_fill_manual("Threshold level", values = wes_palette("Royal2")) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = seq(0,60,10)
                     ) +
  my_ggtheme_p(
    leg_pos = "right",
    ax_tl_s = 14,
    ax_tx_s = 11,
    y_hjust = 1,
    y_vjust = 0.5
    # axx_tx_ang = 45
  )
  
# Save plot 
ggsave("./results/supplements/fig_S2.png",
       last_plot(),
       height = 8,
       width = 8
)
  

```


### Speices list for supplements

```{r}

# Number of straddling species
length(unique(prop_data$taxon_key)) #76
round(76/633 *100) #12

# Number of straddling stocks
prop_data %>% 
  group_by(rfmo_name,realm_name) %>% 
  summarise(x = length(unique(taxon_key)),
            .groups = "keep") %>% 
  pull(x) %>% sum() # 512

straddling_species <- prop_data %>% 
  left_join(exploited_spp) %>% 
  left_join(sau_groups %>% rename(taxon_name = scientific_name)) %>% 
  mutate(commercial_group = ifelse(is.na(commercial_group),"Other fish & inverts",commercial_group)) %>% 
  group_by(taxon_name,common_name,commercial_group) %>% 
  tally() %>% 
  select(-n)

straddling_species %>% 
  pull(commercial_group) %>% 
  unique()


write_csv(straddling_species, "./results/supplements/straddling_species.csv") # this dataset has been further updated online using thesearoundus.org

```


### Straddling species map

```{r straddling_map, eval = T, echo = F}

# Scaling function for plot
scaling <- function(x,...){(x-min(x,...))/(max(x,...)-min(x,...))}

# Get MEOW and EEZs (REMOVE)
# meow_dbem_eez <- meow_dbem_grid %>% 
#   group_by(realm,eez_name) %>% 
#   tally() %>% 
#   select(-n)

# Number of straddling stocks by MEOW
strad_meow <- prop_data %>% 
  group_by(realm_name) %>% 
  summarise(n = length(unique(taxon_key))) %>% 
  mutate(scale_n = scaling(n))

# Number of straddling stocks by RFMO
stradd_rfmo <- prop_data %>% 
  group_by(rfmo_name) %>%
  summarise(n = length(unique(taxon_key))) %>% 
  mutate(scale_n = scaling(n))

# Number of straddling stocks by RFMO and Realm
rfmo_realm <- prop_data %>% 
  group_by(rfmo_name,realm_name) %>% 
  summarise(n = length(unique(taxon_key))) %>% 
  mutate(scale_n = scaling(n))

# Map it
sf_meow_map <- sf_meow %>% 
  group_by(realm_name = realm,rlm_code) %>% 
  tally() %>% 
  select(-n)

map_rfmo_stradd <- ggplot() + 
  geom_sf(data = sf_rfmo %>% left_join(stradd_rfmo), aes(fill = n)) +
  geom_sf(data = sf_meow_map %>% left_join(strad_meow), aes(fill = n)) +
  geom_sf(data = sf_land, aes(), fill = "antiquewhite", color = "grey50") +
  # Add RFMO labels
  geom_label_repel(data = sf_rfmo,
                   aes(label = rfmo_name,
                       geometry = geometry),
                   stat = "sf_coordinates",
                   direction = "y",
                   seed = 5,
                   max.overlaps = 10,
                   point.padding = 50,
                   hjust = "right",
                   nudge_x = 15,
                   nudge_y = ifelse(sf_rfmo$rfmo_name == "CCSBT",-20,-30),
                   alpha = 0.6,
                   size = 4
  ) +
  # geom_label_repel(data = sf_meow_map,
  #                  aes(label = rlm_code,
  #                      geometry = geometry),
  #                  stat = "sf_coordinates",
  #                  alpha = 0.6,
  #                  nudge_x = .15,
  #                  box.padding = 0.5,
  #                  nudge_y = 10,
  #                  segment.ncp = 10,
  #                  segment.angle = 20
  # ) +
  scale_fill_viridis_c("Number of Straddling Stocks", na.value = "white",
                       limits = c(0,50)) +
  my_ggtheme_m(leg_pos = "bottom",
               leg_width = 2) +
  theme(legend.text = element_text(size = 14),
        legend.title = element_text(size = 16))

# Save plot 
ggsave("./results/figures/fig_1a.png",
       map_rfmo_stradd,
       height = 7,
       width = 12
)

```

### Straddling species bar plot

```{r}


# Straddling stocks by RFMO
stradd_commercial <- prop_data %>% 
  left_join(exploited_spp) %>% 
  left_join(sau_groups) %>% 
  group_by(rfmo_name,realm_name,commercial_group) %>% 
  summarise(n = length(unique(taxon_key)),
            species = paste(unique(common_name), collapse = ";"))


stradd_bar_plot <- stradd_commercial %>% 
  filter(n >0,
         !is.na(commercial_group)) %>% 
  mutate(
    realm_name = str_replace(realm_name," ", "\n"),
    realm_name = str_replace(realm_name,"Southern","S."),
    realm_name = str_replace(realm_name,"South","S."),
    realm_name = str_replace(realm_name,"Northern","N."),
    realm_name = str_replace(realm_name, "Western", "W."),
    realm_name = str_replace(realm_name,"Eastern", "E.")
  ) %>% 
  ggplot() +
  geom_bar(
    aes(
      x = commercial_group,
      y = n,
      fill = commercial_group
    ),
    stat = "identity"
  ) +
  facet_grid(rfmo_name~realm_name,
             scales = "free") +
  labs(x = "", y = "Number of straddling stocks") +
  scale_fill_manual("Commercial group",values = c(wes_palette("Darjeeling1")[1:3],
                                                  "grey",
                                                  wes_palette("Darjeeling1")[4:5],
                                                  wes_palette("Darjeeling2"))
                    ) +
  scale_y_continuous(breaks = seq(0,30,5))+
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(),
    strip.background = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 16),
    strip.text = element_text(size = 12),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
    );stradd_bar_plot

# Save plot 
ggsave("./results/figures/fig_1b.png",
       stradd_bar_plot,
       height = 6,
       width = 12
)


```


### Paper numbers on top shared species

```{r}

prop_data %>% 
  left_join(sau_groups) %>% 
  mutate(combo = paste0(realm_name,"_",rfmo_name)) %>% 
  group_by(taxon_name,common_name,commercial_group) %>% 
  summarise(value = length(unique(combo))) %>%
  View()
  top_n(5,value) %>% 
  arrange(desc(value)) %>% 
  View()

  
  
```

## Proportion change

```{r}

# Prepare data
sankey_df <- prop_data %>% 
  group_by(period,rcp,rfmo_name,change,realm_name) %>% 
  tally() %>% 
  # filter(rcp == "rcp85") %>% 
  mutate(
    realm_name = str_replace(realm_name,"Southern","S."),
         realm_name = str_replace(realm_name,"Northern","N."),
         realm_name = str_replace(realm_name, "Western", "W."),
         realm_name = str_replace(realm_name,"Eastern", "E.")
  )




```

## Proportion change table

```{r}


# Total changes

reg_total <- prop_data_esm %>% 
  mutate(change = ifelse(mean > top_tresh,"gain",
                               ifelse(mean < low_tresh,"lost","same")
        )
  ) %>% 
  group_by(period,rcp,rfmo_name,change,realm_name,esm) %>% 
  tally() %>% 
  group_by(rcp,period,esm) %>%
  summarise(total_changes = sum(n))

prop_data_esm %>% 
  mutate(change = ifelse(mean > top_tresh,"gain",
                         ifelse(mean < low_tresh,"lost","same")
  )
  ) %>%
  group_by(period,rcp,rfmo_name,change,realm_name,esm) %>% 
  tally() %>% 
  group_by(rcp,period,esm,change) %>%
  summarise(n = sum(n)) %>%
  left_join(reg_total) %>%
  mutate(per = round(n/total_changes*100)) %>%
  group_by(rcp,period,change) %>%
  summarise_if(is.numeric, c("m" = mean,
                            "sd" = sd)
               ) %>% 
  mutate_if(is.numeric,round) %>% 
  select(1:3,n_m,n_sd,per_m,per_sd) %>% 
  # View()
write_csv("./results/tables/gains_losses.csv")

## Proportion table

  
```

### Circle diagram

Resources:
 - https://r-charts.com/flow/chord-diagram/
 - https://www.data-to-viz.com/graph/chord.html


```{r circle_diagrams, eval = T, echo = T}


  # Color pallet
  mycolor_scale <- 
    c("CCSBT" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[1], 
      "IATTC" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[2], 
      "ICCAT" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[3],
      "IOTC" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[4],
      "WCPFC" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[5],
      "Central\nIndo-Pacific" =  wes_palette("Darjeeling2",n = 5)[2],
      "Temperate\nAustralasia" = wes_palette("Moonrise3",n = 5)[2],
      "Temperate\nSouth America" = wes_palette("Moonrise3",n = 5)[3],
      "S.\nOcean" = wes_palette("Darjeeling2",n = 5)[3],
      "W.\nIndo-Pacific" = wes_palette("Moonrise3",n = 5)[4],
      "E.\nIndo-Pacific" = wes_palette("Moonrise3",n = 5)[5],
      "Tropical\nE. Pacific" = wes_palette("FantasticFox1",n = 5)[1],
      "Arctic" = wes_palette("FantasticFox1",n = 5)[2],
      "Temperate\nN. Atlantic" = wes_palette("FantasticFox1",n =5)[3],
      "Temperate\nS. Africa" = wes_palette("FantasticFox1",n =5)[4],
      "Tropical\nAtlantic" =   wes_palette("FantasticFox1",n =5)[5],
      "Temperate\nN. Pacific" = wes_palette("Darjeeling2", n = 5)[5]
    )

# Run plots

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "ear",change_val = "gain")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "ear",change_val = "lost")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "mid",change_val = "gain")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "mid",change_val = "lost")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "ear",change_val = "same")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "mid",change_val = "same")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "ear",change_val = "net")

lapply(c("rcp26","rcp85"), circular_plot, data = sankey_df, period_val = "mid",change_val = "net")
```


# Supplement material

## RFMO / EEZ map

```{r regional_map, eval = T, echo = F}

regional_map <- ggplot() + 
  geom_sf(data = sf_rfmo, aes(), color = "black", fill = "transparent") +
  geom_sf(data = sf_meow_map, aes(fill = realm_name)) +
  geom_sf_label(data = sf_rfmo, aes(label = rfmo_name)) +
  geom_sf(data = sf_land, aes(), fill = "antiquewhite", color = "grey50") +
  scale_fill_viridis("Region", discrete = T, option = "D") +
  # scale_color_viridis("Region", discrete = T, option = "E") +
  my_ggtheme_m(leg_pos = "bottom")

# Save plot 
ggsave("../results/figures/supplements/regional_map.png",
       regional_map,
       height = 5,
       width = 11
)

```


# Old code 

```{r}



ggplot() +
  geom_sf(data = sf_fao, aes(), fill ="#3B9AB2" ) +
  geom_sf(data = sf_meow %>% group_by(realm) %>% tally(), aes(fill = realm)) +
  geom_sf(data = sf_land, aes(), fill ="grey" ) +
  ggrepel::geom_label_repel(data = sf_fao_lab,
                            aes(label = f_code,
                                geometry = the_geom),
                            stat = "sf_coordinates",
                            direction = "y",
                            seed = 10,
                            point.padding	 = 1,
                            alpha = 0.8,
                            size = 4)


sf_fao_lab <-
  sf_fao %>% 
  group_by(fao_name,f_code) %>% 
  tally() %>% 
  mutate(fao_name_lab = gsub(",","\n",fao_name))

```




### Highly migratpry speices

Annex I Highly migratory species https://www.un.org/depts/los/convention_agreements/texts/unclos/annex1.htm

```{r un_highly_mig_spp, eval = F}

# CANCELLED CHUNK

# List of SAU species
exploited_spp <- my_path("G","SAU", "exploited_species_list.csv", read = T)


# Families
un_families <- c("Bramidae","Alopiidae","Carcharhinidae","Sphyrnidae","Isurida")

for(i in 1:length(un_families)){
  fam <- un_families[i]
  
  fishbase_df <- fb_tbl("species") %>% 
    mutate(Family = fam) %>% 
    select(Genus, Species, FBname, reffered_as = Family) %>% 
    mutate(scientific_name = paste(Genus,Species)) %>% 
    select(scientific_name,reffered_as)
  
  if(i == 1){
    output <-  fishbase_df
  }else{
    output <- bind_rows(output,fishbase_df)
  }
}


un_species <- tibble(scientific_name = c("Thunnus alalunga","Thunnus thynnus","Thunnus obesus", "Katsuwonus pelamis", "Thunnus albacares", "Thunnus atlanticus","Euthynnus alletteratus","Euthynnus affinis", "Thunnus maccoyii",
                                             "Auxis thazard", "Auxis rochei", 
                                             "Tetrapturus angustirostris", "Tetrapturus belone", "Tetrapturus pfluegeri", "Tetrapturus albidus", "Tetrapturus audax", "Tetrapturus georgei", "Makaira mazara", "Makaira indica","Makaira nigricans",
                                             
                                             "Istiophorus platypterus","Istiophorus albicans",
                                             "Xiphias gladius",
                                             "Scomberesox saurus","Cololabis saira","Cololabis adocetus","Scomberesox saurus scombroides",
                                             "Hexanchus griseus", "Cetorhinus maximus", "Rhincodon typus"),
                         reffered_as = c(
                           rep("Tuna",9),
                           "Frigate mackerel","Frigate mackerel",
                           rep("Marlin",9),
                           "Sail-fish","Sail-fish",
                           "Sword-fish",
                           rep("Saury",4),
                           rep("Shark",3)
                         )) %>% 
  mutate(source = "species")



h_migratory_spp <- bind_rows(output,
                             un_species) %>% 
  group_by(scientific_name,source) %>% 
  tally() %>% 
  mutate(cat = "high_mig")

```

### Proportion change map


```{r}
# A function that makes a dataframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=10, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}



plot_data <- prop_data %>% 
  group_by(rfmo_name,realm_name,esm,rcp,change) %>% 
  tally() %>% 
  group_by(realm_name,rfmo_name,rcp,change) %>% 
  summarise(mean_n_shifts = mean(n,na.rm = T)) %>% 
  filter(!is.na(change))


# Get FAO and MEOW centroids

rfmo_centroids <-
  as.data.frame(st_centroid(sf_rfmo)) %>% 
  ungroup() %>% 
  select(rfmo_name, geometry) %>% 
  separate(col = geometry, into = c("lon", "lat"), sep = "\\,")

# Remove "c()"
rfmo_centroids$lon <- gsub("\\(","",rfmo_centroids$lon)
rfmo_centroids$lon <- gsub("c","",rfmo_centroids$lon)
rfmo_centroids$lat <- gsub(")","",rfmo_centroids$lat)


# ggplot() +
#   geom_sf(data = sf_rfmo %>% sf_simplify, aes(), fill ="white" ) +
#   geom_sf(data = sf_land, aes(), fill = "gray30", col = "gray30") +
#   geom_text(data = rfmo_centroids, aes(x = as.numeric(lon), y = as.numeric(lat), label = rfmo_name)) +
#   geom_point(data = rfmo_centroids,
#              aes(
#                x = as.numeric(lon),
#                y = as.numeric(lat),
#                color = rfmo_name
#              )
#   )

# Get MEOW and MEOW centroids

meow_centroids <- as.data.frame(st_centroid(sf_meow)) %>% 
  ungroup() %>% 
  select(realm_name = realm, geometry) %>% 
  separate(col = geometry, into = c("lon", "lat"), sep = "\\,")

# Remove "c()"
meow_centroids$lon <- gsub("\\(","", meow_centroids$lon)
meow_centroids$lon <- gsub("c","", meow_centroids$lon)
meow_centroids$lat <- gsub(")","", meow_centroids$lat)


meow_centroids <- meow_centroids %>% 
  group_by(realm_name) %>% 
  summarise(lon = mean(as.numeric(lon)),
            lat = mean(as.numeric(lat)))

# Modify annolying points (most of them!)
meow_centroids <- meow_centroids %>% 
  mutate(
    lat = ifelse(realm_name == "Temperate Northern Atlantic",72,
               ifelse(realm_name == "Western Indo-Pacific",-9,
                      ifelse(realm_name == "Eastern Indo-Pacific",-4,
                             ifelse(realm_name == "Southern Ocean",-65,
                                    ifelse(realm_name == "Temperate South America",-55,lat
               ))))),
    lon = ifelse(realm_name == "Arctic",-55,
                 ifelse(realm_name == "Temperate Northern Pacific",-130,
                 ifelse(realm_name == "Tropical Eastern Pacific",-90,
                        ifelse(realm_name == "Eastern Indo-Pacific",95,
                               ifelse(realm_name == "Temperate South America",-60,
                                      ifelse(realm_name == "Tropical Atlantic",-55,
                                             ifelse(realm_name == "Temperate North",42,
                                                    ifelse(realm_name == "Temperate Northern Atlantic",42,
                                                           ifelse(realm_name == "Western Indo-Pacific",47,lon
                        )))))))))
  )


# ggplot() +
#   geom_sf(data = sf_meow %>% group_by(realm) %>% tally(), aes(), fill ="white" ) +
#   geom_sf(data = sf_land, aes(), fill = "gray30", col = "gray30") +
#   geom_text(data = meow_centroids, aes(x = as.numeric(lon), y = as.numeric(lat), label = name)) +
#   geom_point(data = meow_centroids,
#              aes(
#                x = as.numeric(lon),
#                y = as.numeric(lat),
#                color = name
#              )
#   ) +
#   geom_point(data = fao_centroids,
#              aes(
#                x = as.numeric(lon),
#                y = as.numeric(lat)
#              )
#   )


# Prepare data from results
Data <-
  plot_data %>% 
  # get coords for sources
  left_join(meow_centroids,
            by = "realm_name") %>%
  rename(start_lon = lon,
         start_lat = lat) %>% 
  # get coords for targets
  left_join(rfmo_centroids,
            by = "rfmo_name") %>%
  rename(
    source = rfmo_name,
    target = realm_name,
         end_lon = lon,
         end_lat = lat) %>% 
  ungroup() %>% 
  drop_na() %>% 
  mutate_at(vars(end_lon,end_lat),as.numeric)

# Get paths data
path_data <- Data 

data_ready_plot=data.frame()

for(i in c(1:nrow(path_data))){
# for(i in 1:4){
  tmp=data_for_connection(path_data$start_lon[i], path_data$start_lat[i], path_data$end_lon[i], path_data$end_lat[i] , i)
  tmp$rcp=path_data$rcp[i]
  tmp$change=path_data$change[i]
  tmp$mean_n_shifts=path_data$mean_n_shifts[i]
  tmp$source=path_data$source[i]
  tmp$objective=path_data$target[i]
  data_ready_plot=rbind(data_ready_plot,tmp)
}


sf_ready_plot <- data_ready_plot %>% 
  st_as_sf(coords = c("lon", "lat")) %>% 
  st_set_crs(4326) #%>% # to match shapefiles
# st_transform(crs = "+proj=eck4") 


# Get arrow data
arrows_data <- as.data.frame(st_coordinates(st_cast(sf_ready_plot,"POINT")$geometry)) %>% 
  bind_cols(data_ready_plot)

ggplot() +
  # geom_sf(data = sf_rfmo, aes(), fill ="white" ) +
  geom_sf(data = sf_meow %>% group_by(realm) %>% tally(), aes()) +
  geom_sf(data = sf_land, aes(), fill = "gray30", col = "gray30") +
  geom_point(data = rfmo_centroids, aes(x = as.numeric(lon), y = as.numeric(lat))) +
  geom_text(data = rfmo_centroids, aes(x = as.numeric(lon), y = as.numeric(lat), label = rfmo_name)) +
  geom_point(data = meow_centroids, aes(x = as.numeric(lon), y = as.numeric(lat))) +
  geom_text(data = meow_centroids, aes(x = as.numeric(lon), y = as.numeric(lat), label = realm_name)) +
  geom_path(data = arrows_data %>% filter(rcp == "rcp85"),
            aes(X, 
                Y,
                group = group,
                color = change,
                size = mean_n_shifts
            ),
            # size = 1,
            arrow = arrow(length = unit(0.01, "npc"),ends = "first"),
            show.legend = NA) +
  facet_wrap(~change,
             ncol =1)



```


## Sankey flow diagram

```{r}


# Prepare data
sankey_df <- prop_data %>% 
  group_by(period,rcp,rfmo_name,change,realm_name) %>% 
  tally() %>% 
  filter(rcp == "rcp85") %>% 
  mutate(
    realm_name = str_replace(realm_name,"Southern","S."),
         realm_name = str_replace(realm_name,"Northern","N."),
         realm_name = str_replace(realm_name, "Western", "W."),
         realm_name = str_replace(realm_name,"Eastern", "E.")
  )

# Get nodes (name of zones)
nodes <- data.frame(name = c(sankey_df %>% ungroup() %>% select(node = realm_name) %>% pull(node) %>% unique(), sankey_df %>% ungroup() %>% select(node = rfmo_name)%>% pull(node) %>% unique()))


# get ids (identify each region by number)
ids <- nodes %>% 
  rowid_to_column("id") %>% 
  rename(realm_name = name) %>% 
  bind_cols(nodes) %>% 
  mutate(
    region = ifelse(name %in% sankey_df$realm_name,"realm_name","rfmo_name")
  ) %>% 
  select(id,realm_name,region)



# Create links (source and target data)
links <- sankey_df %>% 
  left_join(ids,
            by = "realm_name") %>% 
  # View()
  rename(nameb = realm_name) %>%
  rename(realm_name = rfmo_name) %>%
  left_join(ids,
            by = "realm_name") %>% 
  ungroup() %>% 
  filter(period == "mid") %>%
  select(source = id.x,
         target = id.y,
         value = n,
         change,
         everything()
  ) %>%
  mutate(source = source-1,
         target = target - 1)

# Give a color for each group:
# scales::show_col(viridis::viridis_pal(option = "plasma")(10)) # from scales package
# loss 
# same 
# gain 
# Check this for color transparency https://stackoverflow.com/questions/46616321/modify-networkd3-sankey-plot-with-user-defined-colors

 

my_color <- 'd3.scaleOrdinal() .domain(["Arctic","Central Indo-Pacific","Eastern Indo-Pacific","Southern Ocean","Temperate Australasia", "Temperate Northern Atlantic", "Temperate Northern Pacific" , "Temperate South America","Temperate Southern Africa","Tropical Atlantic","Tropical Eastern Pacific","Western Indo-Pacific","Atlantic, Northeast","Atlantic, Northwest","Pacific, Northwest", "Pacific Northeast","Indian Ocean, Eastern","Pacific, Eastern Central","Pacific, Southwest","Pacific, Western Central", "Pacific, Southeast","Indian Ocean, Antarctic","Indian Ocean, Western","Atlantic, Eastern Central","Atlantic, Western Central" ,"Atlantic, Southeast","Atlantic, Southwest"]) .range(["#F98400","#78B7C5","#0B775E"])'

# my_color <- 'd3.scaleOrdinal() .domain(["a", "b"]) .range(["#F98400","#78B7C5","#0B775E"])'


# Plot it!
sankeyNetwork(Links = links,
              Nodes = nodes,
              Source = "source",
              Target = "target",
              Value = "value", 
              NodeID = "name",
              LinkGroup = "change",
              NodeGroup = "name",
              colourScale = my_color,
              fontSize = 15, 
              nodeWidth = 20,
              sinksRight = T
)


# Paper numbers
links %>% 
  group_by(nameb,change) %>% 
  tally() %>% 
  View()


links %>% 
  group_by(nameb,change) %>% 
  summarise(sum(value)) %>% 
  View()

```

### Economic map

```{r}
# Economics

rfmo_catch_country <- rfmo_catch %>% 
  group_by(fishing_entity,commercial_group) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>% 
  mutate(
    value_billion = round(landed_value/10000000000),
    tonnes_million = round(tonnes/1000000,1)
  ) %>% 
  left_join(sau_matching_names) %>% 
  distinct() %>% 
  group_by(iso_a3) %>% 
  summarise_at(.vars = c("tonnes_million","value_billion"),
               .funs = mean,
               na.rm = T
               )


# Make sure everyone is included
# rfmo_catch_country %>% 
#   anti_join(sf_eez,
#             by = "name") %>% 
#   View()

econ_map <- ggplot() +
  geom_sf(data = sf_land, aes(), fill = "antiquewhite", color = "grey50") +
  geom_sf(data = sf_land %>% left_join(rfmo_catch_country, by = "iso_a3"), aes(fill = value_billion))+ scale_fill_viridis_c("Value \n (USD)", na.value = "white") +
  my_ggtheme_m(leg_pos = "right")


# save legend
# legend <- cowplot::get_legend(econ_map)
# ggsave("../results/figures/legend.png", legend, width = 2, height = 2, dpi = 150)
# econ_map <- econ_map + my_ggtheme_m(leg_pos = "")


# Save plot 
ggsave("../results/figures/econ_map.png",
       econ_map,
       height = 5,
       width = 11
)


```

### OHI circle map

```{r}


c_data <- rfmo_catch %>% 
  group_by(area_name,common_name) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>% 
  mutate(
    value_billion = round(landed_value/1000000000),
    tonnes_million = round(tonnes/1000000,1)
  ) %>% 
  select(
    individual = common_name,
    value = value_billion,
    group = area_name
  ) %>% 
  filter(value >0) %>% 
  arrange(group,value)



# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 5
to_add <- data.frame( matrix(NA, empty_bar*length(unique(c_data$group)), ncol(c_data)) )
colnames(to_add) <- colnames(c_data)
to_add$group <- rep(unique(c_data$group), each=empty_bar)
c_data <- rbind(c_data, to_add)
c_data <- c_data %>% arrange(group)
c_data$id <- seq(1, nrow(c_data))

# Get the name and the y position of each label
label_data <- c_data
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- c_data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]


# The plot
ggplot(c_data %>% filter(!is.na(individual)), 
       aes(x = as.factor(id), 
                   y = value, 
                   fill = group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(stat="identity", alpha=0.5) +
   # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 600, xend = start, yend = 600), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 400, xend = start, yend = 400), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
    geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  annotate("text", x = rep(max(c_data$id),4), 
           y = c(0, 200, 400, 600), 
           label = c("0", "200", "400", "600") ,
           color="grey", size=3 , angle=0, fontface="bold", hjust=1) +
  geom_text(data=label_data, aes(x=id, 
                                 y=value+10, 
                                 label=individual,
                                 hjust=hjust), 
            color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE ) +
  ylim(-100,600) +
  # theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar()

ggsave("../results/figures/circular_test.png",
       last_plot(),
       width = 7,
       height = 7)


```


## Catch and value

Catch and value data from the Sea Around Us as an average from 2007 to 2016

### By RFMO

```{r}

# total catch
sum(rfmo_catch$tonnes)/1000000 #million tones
sum(rfmo_catch$landed_value)/1000000000 #million tones


# Catch and value by RFMO
rfmo_catch %>% 
  group_by(area_name) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>% 
  mutate(
    value_billion = round(landed_value/1000000000),
    tonnes_million = round(tonnes/1000000,1)
  ) %>% 
  arrange(desc(value_billion))

```


### By commercial group

```{r}

# Catch and value by RFMO
rfmo_catch %>%
  group_by(commercial_group) %>%
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>%
  mutate(
    value_billion = round(landed_value/1000000000),
    tonnes_million = round(tonnes/1000000,1)
  ) %>%
  arrange(desc(value_billion))

```

### By country

```{r}

# Catch and value by RFMO
rfmo_catch %>% 
  group_by(fishing_entity) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>% 
  mutate(
    value_billion = round(landed_value/1000000000),
    tonnes_million = round(tonnes/1000000,1)
  ) %>% 
  arrange(desc(value_billion))

```


### Circular SAU catch and Revenue

#### All species

```{r}
Species_Data <- rfmo_catch %>% 
  group_by(common_name = fishing_entity,
           rfmo_name = area_name) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>% 
  select(common_name,rfmo_name,value = tonnes) %>% 
  filter(!is.na(value)) %>% 
  arrange(desc(value)) %>% 
  group_by(rfmo_name) %>% 
  top_n(25,value) %>% 
  mutate(
    # value = round(value/10000000000,4),
    value = round(value/100000,4)
  )

# Species_Data <- shared_data %>%
#   mutate(combo = paste0(realm,"_",rfmo_name)) %>%
#   group_by(group = common_name,rfmo_name) %>%
#   summarise(value = length(unique(combo))) %>%
#   top_frac(.5)


label_data <- Species_Data

# Set a number of 'empty bar' to add at the end of each group
Char <- as.factor(Species_Data$rfmo_name)
empty_bar <- 5
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$rfmo_name <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(rfmo_name,value)
Species_Data$id <- seq(1, nrow(Species_Data))


# Get the name and the y position of each label
# Create labels for all but top 5
label_data <- Species_Data
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- Species_Data %>% 
  group_by(rfmo_name) %>% 
  summarize(start=min(id), 
            end=max(id) - empty_bar, 
            median = median(value, na.rm = T)
  ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)),
         label = str_extract(rfmo_name, '\\b[^,]+$'))


# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
# grid_data <- grid_data[-1,]
grid_data[1,2] <- 5 # Manually include bathydemerssal
grid_data[1,3] <- 1 

# Median data
median_data <- grid_data %>% 
  mutate_at(vars(start,end),
            .funs = as.numeric)

# Seq_axis_spp <- seq(0,30,10)
Seq_axis_spp <- seq(0,15,5)
Plot_Limit <- max(Species_Data$value,na.rm=T)
Ticks_Color <- "black"
  


Spp_circular <-
ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=rfmo_name)
) +       
  # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=rfmo_name),
           stat="identity",
           alpha=0.5) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  # geom_segment(data=grid_data,
  #              aes(x = end, y = 30, xend = start, yend = 30),
  #              colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  # geom_segment(data=grid_data,
  #              aes(x = end, y = 20, xend = start, yend = 20),
  #              colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data,
               aes(x = end, y = 15, xend = start, yend = 15),
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data, 
               aes(x = end, y = 10, xend = start, yend = 10),  
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data,
               aes(x = end, y = 05, xend = start, yend = 05),
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  # Add median lines for each gropup
  geom_segment(data=median_data,
               aes(x = end, y = median, xend = start+5, yend = median, colour = rfmo_name),
               alpha=1, size=0.5 , inherit.aes = FALSE) +
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Species_Data$id),4),
           y = Seq_axis_spp,
           label = Seq_axis_spp,
           color=Ticks_Color, 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=rfmo_name),
           stat="identity",
           alpha=0.5) +
  # Species names
  geom_text(data=label_data,
            aes(x=id, 
                # y= 30,
                y= 16,
                label = common_name,
                hjust = hjust), 
            color="black",
            fontface="italic",
            alpha=1,
            size=3,
            angle= label_data$angle,
            inherit.aes = FALSE) +
  # ylim(-10,40) +
  ylim(-10,40) +
  theme_bw() +
  theme(
    # legend.position = c(0.75,0.25),
    # legend.position = c(0.50,0.50),
    legend.position = "",
    legend.text = element_text(size = 7),
    legend.title.align = 0.5,
    legend.title = element_text(size = 12, face = "bold"),
    legend.key = element_rect(colour = NA, fill = NA),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    panel.border   = element_blank(),
    
  ) +
  coord_polar() +
  scale_fill_viridis("RFMO",option= "D", discrete = T) +
  scale_color_viridis("RFMO",option= "D", discrete = T) +
  guides(fill=guide_legend(ncol=1))

# save legend
# legend <- cowplot::get_legend(Spp_circular)
# ggsave("../results/figures/legend.png", legend, width = 2, height = 2, dpi = 150)
# Spp_circular <- Spp_circular + theme(legend.position = "legend.position")


# Save plot
ggsave(filename = name_save,
       plot = last_plot(),
       width = 8,
       height = 8,
       units = "in")
```


#### Tunas 


```{r}

top_10_coiuntries <- rfmo_catch %>% 
  filter(commercial_group == "Tuna & billfishes") %>% 
  group_by(fishing_entity) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>%
  # group_by(fishing_entity) %>%
  arrange(landed_value) %>%
  top_n(10,landed_value)

totals <- rfmo_catch %>% 
  filter(commercial_group == "Tuna & billfishes") %>% 
  gather("category","value",tonnes,landed_value) %>% 
  group_by(category) %>% 
  summarise_if(is.numeric,c("tot"=sum))


top_10_coiuntries %>% 
  # filter(fishing_entity %in% c("Indonesia","Japan","Philippines")) %>% 
  gather("category","value",tonnes,landed_value) %>% 
  left_join(totals) %>% 
  mutate(per = (value/tot)*100) %>% 
  View()
  group_by(category) %>% 
  summarise_if(is.numeric,sum)

round(563715940668/1000000000)
3521510/1000000

tunas <- c("Albacore","Bigeye tuna","Pacific bluefin tuna","Skipjack tuna","Southern bluefin tuna","Yellowfin tuna")


Species_Data <- rfmo_catch %>% 
  filter(commercial_group == "Tuna & billfishes",
         fishing_entity %in% top_10_coiuntries$fishing_entity) %>% 
  mutate(common_name = ifelse(common_name %in% tunas, common_name,"Other billfishes")) %>% 
  group_by(common_name,
           fishing_entity#,
           # rfmo_name = area_name
           ) %>% 
  summarise_at(
    .vars = c("tonnes","landed_value"),
    .funs = sum,
    na.rm = T
  ) %>%
  # mutate(price_per_kilo = landed_value/tonnes) %>% 
  gather("category","value",tonnes:landed_value) %>%
  filter(!is.na(value)) %>%
  mutate(
  value = ifelse(category == "landed_value", round(value/1000000000,4),round(value/1000,4)),
  category = ifelse(category == "tonnes","Catch (thousand tonnes)","Value (billion USD)")
  )


ggplot(Species_Data) +
  geom_bar(
    aes(
      x = reorder(fishing_entity,-value),
      y = value,
      fill = reorder(common_name,value)
    ),
    stat = "identity"
  ) +
  coord_flip() +
  facet_wrap(~category,
             scales = "free_x") +
  scale_fill_manual("Species ",values = c(wes_palette("Darjeeling1"),wes_palette("Darjeeling2"))) +
  labs(x = "Country",
       y = "Value") +
  my_ggtheme_p(
  leg_pos = "right",
  leg_tl_s = 12,
  leg_tx_s = 10,
  facet_tx_s = 11,
  ax_tx_s = 11,
  ax_tl_s = 12
  )


# Save plot
ggsave(filename = "./results/figures/top10_tuna.png",
       plot = last_plot(),
       width = 10,
       height = 5,
       units = "in")


# Categories dominating 
Species_Data %>% 
  group_by(common_name,category) %>% 
  summarise(sum(value)) %>% 
  View()

```

# Old code for cicrlce plots

```{r}


# Gain Data
circle_data <-
  sankey_df %>% 
  filter(
    period == period_val,
    rcp == rcp_val,
    change == change_val
         ) %>% 
  mutate(name = str_replace(realm_name," ", "\n")) %>% 
  ungroup() %>% 
  select(rowname = name,
         key = rfmo_name,
         value = n)

# Color pallet
mycolor_scale <- 
  c("CCSBT" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[1], 
    "IATTC" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[2], 
    "ICCAT" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[3],
    "IOTC" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[4],
    "WCPFC" = viridis(8, alpha = 1, begin = 0, end = 1, option = "D")[5],
    "Central\nIndo-Pacific" =  wes_palette("Darjeeling2",n = 5)[2],
    "Temperate\nAustralasia" = wes_palette("Moonrise3",n = 5)[2],
    "Temperate\nSouth America" = wes_palette("Moonrise3",n = 5)[3],
    "S. Ocean" = wes_palette("Darjeeling2",n = 5)[3],
    "W.\nIndo-Pacific" = wes_palette("Moonrise3",n = 5)[4],
    "E.\nIndo-Pacific" = wes_palette("Moonrise3",n = 5)[5],
    "Tropical\nE. Pacific" = wes_palette("FantasticFox1",n = 5)[1],
    "Arctic" = wes_palette("FantasticFox1",n = 5)[2],
    "Temperate\nN. Atlantic" = wes_palette("FantasticFox1",n =5)[3],
    "Temperate\nS. Africa" = wes_palette("FantasticFox1",n =5)[4],
    "Tropical\nAtlantic" =   wes_palette("FantasticFox1",n =5)[5],
    "Temperate\nN. Pacific" = wes_palette("Darjeeling2", n = 5)[5]
  )


name <- paste0("./results/figures/circular_",change_val,"_",period_val,"_",rcp_val,".png")
png(name,
    width = 1300, height = 1300, res = 150, units = "px")

chordDiagram(
  x = circle_data %>% arrange(rowname), 
  grid.col = mycolor_scale,
  directional = ifelse(change_val == "gain",1, -1),
  direction.type = c("diffHeight","arrows"),
  link.arr.type = "big.arrow",
  link.arr.length = 0.1,
  link.sort = T,
  link.auto = T,
  link.largest.ontop = TRUE,
  transparency = 0.30,
  scale = T,
  symmetric = T,
  big.gap = 5
)
dev.off()


# Net Change Data
net_change <-
  sankey_df %>% 
  pivot_wider(
    names_from = change,
    values_from = n) %>% 
  mutate_at(.var = c("gain","lost"),
            .funs = replace_na,0
  ) %>% 
mutate(name = str_replace(realm_name," ", "\n"),
       value = gain - lost,
       rowname_b = ifelse(value > 0,name,rfmo_name),
       key_b = ifelse(value < 0,name,rfmo_name)) %>% 
    # View()
  ungroup() %>%
  mutate(
    n_shifting = gain+lost,
    per = value/(n_shifting),
    per_non = same/(gain+lost+same)*100
    ) %>% 
  # View()
  filter(period == period_val,
         rcp == rcp_val) %>% 
  select(rowname = rowname_b,
         key = key_b,
         value) %>% 
  filter(value != 0)



name_net <- paste0("./results/figures/circular_net_",period_val,"_",rcp_val,".png")
png(name_net,
    width = 1300, height = 1300, res = 150, units = "px")

chordDiagram(
  x = net_change, 
  grid.col = mycolor_scale,
  directional = 1, 
  direction.type = c("diffHeight","arrows"),
  link.arr.type = "big.arrow",
  link.arr.length = 0.1,
  link.sort = F,
  link.largest.ontop = TRUE,
  transparency = 0.30,
  scale = F,
  symmetric = F
  )
dev.off() 


```



### Circle For Tunas

```{r}

# Prepare data
sankey_df <- prop_data %>% 
  filter(common_name %in% c("Albacore","Bigeye tuna","Pacific bluefin tuna","Skipjack tuna","Southern bluefin tuna","Yellowfin tuna")) %>% 
  group_by(period,rcp,rfmo_name,change,realm_name) %>% 
  tally() %>% 
  mutate(
    realm_name = str_replace(realm_name,"Southern","S."),
         realm_name = str_replace(realm_name,"Northern","N."),
         realm_name = str_replace(realm_name, "Western", "W."),
         realm_name = str_replace(realm_name,"Eastern", "E.")
  )


# Net Change Data
net_change <-
  sankey_df %>% 
  pivot_wider(
    names_from = change,
    values_from = n) %>% 
  mutate(gain = ifelse(is.na(gain),0,gain),
         lost = ifelse(is.na(lost),0,lost)) %>% 
mutate(name = str_replace(realm_name," ", "\n"),
         value = gain - lost,
       rowname_b = ifelse(value > 0,name,rfmo_name),
       key_b = ifelse(value < 0,name,rfmo_name)) %>% 
# Uncomment for overall numbers
  # group_by(period,rcp) %>%
  # summarise_at(c("gain","lost","same"),
  #              .funs = sum,
  #              na.rm = T) %>%
  # mutate(per_change = 100-same/(gain+lost+same)*100)
  ungroup() %>% 
  select(rowname = rowname_b,
         key = key_b,
         value) %>% 
  filter(value != 0,
         period == "ear",
         rcp == "rcp85") 

length(unique(net_change$key))
length(unique(net_change$rowname))

mycolor_g <- c(viridis(10, alpha = 1, begin = 0, end = 1, option = "D"),
             viridis(5, alpha = 1, begin = 0, end = 1, option = "F")
             )


png("./results/figures/circular_net_tuna.png", width = 1200, height = 1200, res = 150, units = "px")
chordDiagram(
  x = net_change, 
  grid.col = mycolor_g,
  directional = 1, 
  direction.type = c("diffHeight","arrows"),
  link.arr.type = "big.arrow",
  link.arr.length = 0.1,
  link.sort = F,
  link.largest.ontop = TRUE,
  transparency = 0.30,
  scale = F,
  symmetric = F
  )
dev.off() 


```



### Intensity

```{r}

sankey_df <- prop_data %>% 
  mutate(range = ifelse(change == "gain",mean-low_tresh,
                        ifelse(change == "same",NA,mean-top_tresh)
                        ) 
         ) %>% 
  filter(!is.na(range)) %>%
  # View()
  group_by(common_name,period,rcp,rfmo_name,realm_name) %>% 
  summarise(range_m = mean(range, na.rm =T)) %>% 
  group_by(period,rcp,rfmo_name,realm_name) %>% 
  summarise(range_m = mean(range_m, na.rm =T)) %>% 
  filter(rcp == "rcp85") %>% 
  mutate(
    realm_name = str_replace(realm_name,"Southern","S."),
         realm_name = str_replace(realm_name,"Northern","N."),
         realm_name = str_replace(realm_name, "Western", "W."),
         realm_name = str_replace(realm_name,"Eastern", "E.")
  )

# Gain Data
circle_data <-
  sankey_df %>% 
  filter(
    period == "ear"
    # change == "lost"
         ) %>% 
  mutate(name = str_replace(realm_name," ", "\n")) %>% 
  ungroup() %>% 
  select(rowname = name,
         key = rfmo_name,
         value = range_m)


png("./results/figures/circular_range.png", width = 1200, height = 1200, res = 150, units = "px")
chordDiagram(
  x = circle_data, 
  grid.col = mycolor_g,
  directional = -1, 
  direction.type = c("diffHeight","arrows"),
  link.arr.type = "big.arrow",
  link.arr.length = 0.1,
  link.sort = F,
  link.largest.ontop = TRUE,
  transparency = 0.30,
  scale = F,
  symmetric = F
  )
dev.off() 

```